A Simple and Strong Baseline for Universal Targeted Attacks on Siamese Visual Tracking

### 2021-09-24 博士/论文提交/adversarial_attack/TCSVT/大修/response/response.tex

\textbf{
Thanks for your advice.
% 承认已有问题：相比于现有的目标跟踪攻击算法，我们方法的不足之处是扰动值较为显眼。
The shortcoming of our method is the more conspicuous perturbation values compared to existing target tracking attack algorithms.
% 解释我们的扰动显眼的原因：其他方法在整个搜索图像添加扰动，而我们必须要在$64 \times 64$这个很小的区域内添加扰动，这增加了学习的难度，使得扰动值大。
Other methods add perturbations over the entire search image, whereas we need to add perturbations over a very small region of $64 \times 64$, which increases the learning difficulty and makes the perturbation values large.
% 解释我们不用全图攻击的原因：我们仅在小区域内而不是在整个搜索图像上添加扰动，因为必须指定轨迹在哪。
% 解决方案：为了既享受全图扰动带来的低感知性，以及局部扰动用于指定目标位置，我们考虑在不同的图像通道执行不同的扰动：首先将图像转为YCbCr通道，在Y通道做全图攻击，在CbCr通道做局部攻击。or: 为了在有目标攻击的同时降低可感知性，...
To reduce perceptibility while achieving the targeted attack, we consider a new way to perturb the search image: first we convert the search image into YCbCr color space, then add perturbations over the entire search image in the Y channel, and add perturbations over a very small region of $64 \times 64$ in the CbCr channel.
% 介绍什么是 YCbCr
Different from RGB color space, YCbCr color space encodes a color image similar to human eyes’ retina, which separates the RGB components into a luminance component (Y) and two chrominance components (Cb as blue projection and Cr as red projection).
% 解释为什么用YCbCr而不是RGB。选择 YCbCr 而不是 RGB 的原因是更加独立。
We choose YCbCr color space since its color channels are less correlated and quite independent than RGB.
% 解释为什么在CbCr上做局部攻击在Y上做全图攻击，而不是其他方式：有研究证明Y通道可感知性更强而CbCr弱一些。因为我们希望补丁区域扰动值更小，所以我们在CbCr做局部攻击。
While considering the color sensitivity of human vision system, the CbCr channels are less sensitive than the Y channel. This means that the patch added in the CbCr channels has better performance of transparency.
% 实验细节：迭代了多少次？损失函数各项的权重是什么？模板图像怎么操作。
% 实验结果。
The detailed analysis of new added experiment is added in Section IV.D of the revised manuscript.
For your convenience in cross-checking, the new text is given as follows.}

\begin{figure}[t]
  \renewcommand\thefigure{9}
  \centering
  \includegraphics[width=.8\textwidth]{images_imperceptible/1.pdf}
  \caption{Visualization of the perturbations.
  % 介绍什么是 RGB Attack
  Figure (a) demonstrates the perturbations trained by the RGB attack method, i.e., the attack method proposed in Section III.
  % 介绍什么是 YCbCr Attack
  Figure (b) demonstrates the perturbations trained by the YCbCr attack method: first we convert the search image into YCbCr color space, then add perturbations over the entire search image in the Y channel, and add perturbations over a very small region of $64 \times 64$ in the CbCr channel. 
  For the template image, we convert it into YCbCr color space, then add the perturbation over the entire template image in all YCbCr channels.
  The perturbed template and search images are then converted into RGB color space and fed into the tracking network.
  The other steps of the training process are the same as the attack method in Section III.
  Attacking the YCbCr color space brings better imperceptibility. Compared with attacking the RGB space, the SSIM of $p$ increases from 0.56 to 0.78. The SSIM of $\delta$ remains unchanged at 0.79.}
  \label{fig:YCbCr}
\end{figure}

\begin{table}[t]
  \renewcommand\thetable{XI}
  \centering
  \caption{Influence of different ways to perturb the search image. The first row demonstrates the attack performance of the RGB attack method, i.e., the attack attack method proposed in Section III. The second row demonstrates the attack performance of YCbCr attack method: first we convert the search image into YCbCr color space, then add perturbations over the entire search image in the Y channel, and add perturbations over a very small region of $64 \times 64$ in the CbCr channel. The attack performance is evaluated according to AO/SR on GOT-Val.}
  \label{table:perturb}
  \begin{tabular}{@{}rcccccc@{}}
  \toprule
  \multirow{2}{*}[-1pt]{\begin{tabular}[c]{@{}c@{}}Way to perturb\\ the search image\end{tabular}} & \multicolumn{2}{c}{Untargeted Attack} & \multicolumn{2}{c}{Targeted Attack} & \multicolumn{2}{c}{SSIM} \\ \cmidrule{2-7}
                                                         & AO                                      & SR                               & AO                & SR                   & $\delta$          & $p$  \\ \midrule
  RGB Attack                                             & 0.153                                   & 0.123                            & 0.840             & 0.890                & 0.56              & 0.79 \\
  YCbCr Attack                                           & 0.246                                   & 0.227                            & 0.682             & 0.756                & 0.78              & 0.79 \\ \bottomrule        
  \end{tabular}
\end{table}

@@

% \begin{table}[]
%   \begin{tabular}{lllllll}
%   \caption{Performance of the new attack method. We can see SSIM increases.}
%           & \multicolumn{2}{l}{Untargeted Attack} & \multicolumn{2}{l}{Targeted Attack} & \multirow{2}{*}{SSIM x} & \multirow{2}{*}{SSIM z} \\
%           & AO                & SR                & AO               & SR               &                         &                         \\
%   method1 & 0.1747            & 0.1442            & 0.8448           & 0.8972           & 0.56                    & 0.79                    \\
%   method2 &                   &                   &                  &                  & 0.78                    & 0.79                   
%   \end{tabular}
% \end{table}

%%%% 问题 3.2 %%%%
\textit{2. The proposed method and offline training phase should be explained more clearly. For instance, the termination of offline training or offline optimization is missed affecting perturbation values.}

\textbf{Thanks for the good comment. As suggested, we have explained in detail the perturbation update process in offline training.
The detailed analysis is added in Section III.B of the revised manuscript.
For your convenience in cross-checking, the new text is given as follows.}

\uline{Before introducing the perturbation update process in offline training, we first revisit the popular adversarial example generation methods. One of the simplest methods to generate adversarial images $I^{adv}$ works by linearizing loss function in $L_{\infty}$ neighbourhood of a clean image and finds exact maximum of linearized function using following closed-form equation \cite{FGSM}:}
\begin{equation}
    I^{adv} = I + \epsilon \cdot \text{ sign} \bigl( \nabla_I L(I, y_{true})  \bigr),
    \vspace{-0.1cm}
\end{equation}
\uline{where $I$ is the input image, and the values of the pixels are integer numbers in the range [0, 255]. $y_{true}$ is the true label for the image $I$. $L(I, y)$ is the cost function of the neural network for the attack purpose, given image $I$ and label $y$. $\epsilon$ is a hyper-parameter to be chosen. A straightforward way to extend the above method is applying it multiple times with small step size. This leads to the Basic Iterative Method (BIM) introduced in \cite{DBLP:conf/iclr/KurakinGB17a}:}
\begin{equation}
    \begin{gathered}
        I_0^{adv} = I, \\
        I_{N+1}^{adv} = I_N^{adv}+\epsilon \cdot \text{ sign}(\nabla_I L(I_N^{adv},y_{true})),
    \end{gathered}
\end{equation}
%\uline{where $Clip_{I, \epsilon} \left\{ I' \right\}$ is the function which performs per-pixel clipping of the image $I'$, so that the result will be in $L_{\infty}$ $\epsilon$-neighbourhood of the source image $I$.}
\uline{The BIM can be easily made into an attacker for a specific desired target class, called the Iterative Target Class Method \cite{DBLP:conf/iclr/KurakinGB17a}:}
\begin{equation}
  \begin{gathered}
      I_0^{adv} = I,\\
      I_{N+1}^{adv} = I_N^{adv}-\epsilon \cdot \text{ sign}(\nabla_I L(I_N^{adv},y_{target})).
  \end{gathered}
  \label{equ:itcm}
\end{equation}

### 2021-09-24 博士/论文提交/adversarial_attack/TCSVT/大修/正文/main.tex
改错字

%%%%%%%% 消融实验：YCbCr攻击 %%%%%%%%
\begin{table}[t]
  \centering
  \caption{Influence of different ways to perturb the search image. The first row demonstrates the the attack performance of the RGB attack method, i.e., the attack attack method proposed in Section III. The second row demonstrates the attack performance of YCbCr attack method: first we convert the search image into YCbCr color space, then add perturbations over the entire search image in the Y channel, and add perturbations over a very small region of $64 \times 64$ in the CbCr channel. The attack performance is evaluated according to AO/SR on GOT-Val.}
  \label{table:perturb}
  \begin{tabular}{@{}rcccccc@{}}
  \toprule
  \multirow{2}{*}[-1pt]{\begin{tabular}[c]{@{}c@{}}Way to perturb\\ the search image\end{tabular}} & \multicolumn{2}{c}{Untargeted Attack} & \multicolumn{2}{c}{Targeted Attack} & \multicolumn{2}{c}{SSIM} \\ \cmidrule{2-7}
                                                         & AO                                      & SR                               & AO                & SR                   & $\delta$          & $p$  \\ \midrule
  RGB Attack                                             & 0.153                                   & 0.123                            & 0.840             & 0.890                & 0.56              & 0.79 \\
  YCbCr Attack                                           & 0.246                                   & 0.227                            & 0.682             & 0.756                & 0.78              & 0.79 \\ \bottomrule        
  \end{tabular}
\end{table}
\uline{\textit{Ablation Study: Attack in YCbCr Space}
The shortcoming of our method is the more conspicuous perturbation values compared to existing target tracking attack algorithms. Other methods add perturbations over the entire search image, whereas we need to add perturbations over a very small region of $64 \times 64$, which increases the learning difficulty and makes the perturbation values large. To reduce perceptibility while achieving the targeted attack, we consider a new way to perturb the search image: first we convert the search image into YCbCr color space, then add the perturbation over the entire search image in the Y channel, and add perturbations over a very small region of $64 \times 64$ in the CbCr channel. Different from RGB color space, YCbCr color space encodes a color image similar to human eyes’ retina, which separates the RGB components into a luminance component (Y) and two chrominance components (Cb as blue projection and Cr as red projection). We choose YCbCr color space since its color channels are less correlated and quite independent than RGB \cite{8630918}. While considering the color sensitivity of human vision system, the CbCr channels are less sensitive than the Y channel \cite{8630918}. This means that the patch added in the CbCr channels has better performance of transparency.
For the template image, we convert it into YCbCr color space, then add the perturbation over the entire template image in all YCbCr channels. The perturbed template and search images are then converted into RGB color scpace and fed into the tracking network. The other steps of the training process are the same as the attack method in Section III. The experimental result is shown in Table \ref{table:perturb}. As we can see, the performance of attacking the YCbCr color space is slightly degraded compared to attacking the RGB color space. Specifically, in terms of AO on GOT-VAL, the targeted attack performance is 0.680, and the untargeted attack performance is 0.246. However, attacking the YCbCr color space brings better imperceptibility (see Figure \ref{fig:YCbCr}). Compared with attacking the RGB space, the SSIM of $p$ increases from 0.56 to 0.78. The SSIM of $\delta$ remains unchanged at 0.79.
}

\begin{figure}[t]
  \centering
  \includegraphics[width=0.48\textwidth]{images_imperceptible/1.pdf}
  \caption{\uline{Visualization of the perturbations.
  % 介绍什么是 RGB Attack
  Figure (a) demonstrates the pereturbations trained by the RGB attack method, i.e., the attack attack method proposed in Section III.
  % 介绍什么是 YCbCr Attack
  Figure (b) demonstrates the perturbations trained by the YCbCr attack method: first we convert the search image into YCbCr color space, then add pereturbations over the entire search image in the Y channel, and add perturbations over a very small region of $64 \times 64$ in the CbCr channel. 
  For the template image, we convert it into YCbCr color space, then add the perturbation over the entire template image in all YCbCr channels.
  The perturbed template and search images are then converted into RGB color scpace and fed into the tracking network.
  The other steps of the training process are the same as the attack method in Section III.
  Attacking the YCbCr color space brings better imperceptibility. Compared with attacking the RGB space, the SSIM of $p$ increases from 0.56 to 0.78. The SSIM of $\delta$ remains unchanged at 0.79.}
  }
  \label{fig:YCbCr}
\end{figure}

>>>>

%%%%%%%% 消融实验：YCbCr攻击 %%%%%%%%
\begin{table}[t]
  \centering
  \caption{Influence of different ways to perturb the search image. The first row demonstrates the attack performance of the RGB attack method, i.e., the attack method proposed in Section III. The second row demonstrates the attack performance of YCbCr attack method: first we convert the search image into YCbCr color space, then add perturbations over the entire search image in the Y channel, and add perturbations over a very small region of $64 \times 64$ in the CbCr channel. The attack performance is evaluated according to AO/SR on GOT-Val.}
  \label{table:perturb}
  \begin{tabular}{@{}rcccccc@{}}
  \toprule
  \multirow{2}{*}[-1pt]{\begin{tabular}[c]{@{}c@{}}Way to perturb\\ the search image\end{tabular}} & \multicolumn{2}{c}{Untargeted Attack} & \multicolumn{2}{c}{Targeted Attack} & \multicolumn{2}{c}{SSIM} \\ \cmidrule{2-7}
                                                         & AO                                      & SR                               & AO                & SR                   & $\delta$          & $p$  \\ \midrule
  RGB Attack                                             & 0.153                                   & 0.123                            & 0.840             & 0.890                & 0.56              & 0.79 \\
  YCbCr Attack                                           & 0.246                                   & 0.227                            & 0.682             & 0.756                & 0.78              & 0.79 \\ \bottomrule        
  \end{tabular}
\end{table}
\uline{\textit{Ablation Study: Attack in YCbCr Space}
The shortcoming of our method is the more conspicuous perturbation values compared to existing target tracking attack algorithms. Other methods add perturbations over the entire search image, whereas we need to add perturbations over a very small region of $64 \times 64$, which increases the learning difficulty and makes the perturbation values large. To reduce perceptibility while achieving the targeted attack, we consider a new way to perturb the search image: first we convert the search image into YCbCr color space, then add the perturbation over the entire search image in the Y channel, and add perturbations over a very small region of $64 \times 64$ in the CbCr channel. Different from RGB color space, YCbCr color space encodes a color image similar to human eyes’ retina, which separates the RGB components into a luminance component (Y) and two chrominance components (Cb as blue projection and Cr as red projection). We choose YCbCr color space since its color channels are less correlated and quite independent than RGB \cite{8630918}. While considering the color sensitivity of human vision system, the CbCr channels are less sensitive than the Y channel \cite{8630918}. This means that the patch added in the CbCr channels has better performance of transparency.
For the template image, we convert it into YCbCr color space, then add the perturbation over the entire template image in all YCbCr channels. The perturbed template and search images are then converted into RGB color space and fed into the tracking network. The other steps of the training process are the same as the attack method in Section III. The experimental result is shown in Table \ref{table:perturb}. As we can see, the performance of attacking the YCbCr color space is slightly degraded compared to attacking the RGB color space. Specifically, in terms of AO on GOT-VAL, the targeted attack performance is 0.680, and the untargeted attack performance is 0.246. However, attacking the YCbCr color space brings better imperceptibility (see Figure \ref{fig:YCbCr}). Compared with attacking the RGB space, the SSIM of $p$ increases from 0.56 to 0.78. The SSIM of $\delta$ remains unchanged at 0.79.
}

\begin{figure}[t]
  \centering
  \includegraphics[width=0.48\textwidth]{images_imperceptible/1.pdf}
  \caption{\uline{Visualization of the perturbations.
  % 介绍什么是 RGB Attack
  Figure (a) demonstrates the pereturbations trained by the RGB attack method, i.e., the attack method proposed in Section III.
  % 介绍什么是 YCbCr Attack
  Figure (b) demonstrates the perturbations trained by the YCbCr attack method: first we convert the search image into YCbCr color space, then add pereturbations over the entire search image in the Y channel, and add perturbations over a very small region of $64 \times 64$ in the CbCr channel. 
  For the template image, we convert it into YCbCr color space, then add the perturbation over the entire template image in all YCbCr channels.
  The perturbed template and search images are then converted into RGB color space and fed into the tracking network.
  The other steps of the training process are the same as the attack method in Section III.
  Attacking the YCbCr color space brings better imperceptibility. Compared with attacking the RGB space, the SSIM of $p$ increases from 0.56 to 0.78. The SSIM of $\delta$ remains unchanged at 0.79.}
  }
  \label{fig:YCbCr}
\end{figure}
